Data preparation

### 2020-07-24 production/prod_prep-data.rmd

```{r}
#library(datasets)
#library(data.table)
#wide <- setDT(wide02)
#long01<- melt(wide,variable.name = "wave",
#              measure = patterns("^perc_effort_","^perc_talent_","^perc_wpart_","^perc_netw_",
#                                       "^pref_effort_","^pref_talent_","^pref_wpart_","^pref_netw_",
#                                       "^sexo_","^edad_","^edcep_"),
#              value.name = c("perc_effort","perc_talent","perc_wpart","perc_netw",
#                             "pref_effort","pref_talent","pref_wpart","pref_netw",
#                             "sexo","edad","edcep"))
```

>>>>

```{r}
library(datasets)
library(data.table)
wide <- setDT(wide02)
long01<- melt(wide,variable.name = "wave",
              measure = patterns("^perc_effort_","^perc_talent_","^perc_wpart_","^perc_netw_",
                                       "^pref_effort_","^pref_talent_","^pref_wpart_","^pref_netw_",
                                       "^sexo_","^edad_","^edcep_"),
              value.name = c("perc_effort","perc_talent","perc_wpart","perc_netw",
                             "pref_effort","pref_talent","pref_wpart","pref_netw",
                             "sexo","edad","edcep"))
```
